---
title: "title"
author: "alikat"
date: "2024-09-03"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Set up a vector named age
```{r}
age=c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41, 51, 35, 24, 33, 41)
```
# a.How many data points?

```{r}
length(age)
```
# 34 data points

# 2.Find the reciprocal of the values for age.
```{r}
reciprocal <- 1/age
print (reciprocal)
```
# 3. Assign also new_age <- c(age, 0, age).
```{r}
new_age <- c(age, 0, age)
print (new_age)
```
# The values of the new_age has the same values with the age.

# 4. Sort the values for age.
```{r}
sort(age)
```
# 5. Find the minimum and maximum value for age.
```{r}
min(age)
max(age)
```
# 17 is the minimum
# 57 is the maximum

# 6. Set up a vector named data.
```{r}
data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5, 2.3, 2.5, 2.3, 2.4, 2.7)
```
# a.How many data points?
```{r}
length(data)
```
# 12 data points

# 7. What happen to the data?

```{r}
new_vector <- data
data * 2
```
# the data vector results in a new vector where each element is twice the original value.

# 8.1. Integers from 1 to 100.
```{r}
m <- seq(1:100)
print(m)
```
# 8.2. Numbers from 20 to 60
```{r}
a <- seq(20,60)
print(a)
```
# 8.3. Mean of numbers from 20 to 60
```{r}
r <- mean(20,60)
print(r)
```
# 8.4. Sum of numbers from 51 to 91
```{r}
i <- sum(51:91)
print(i)
```
# 8.5. Integers from 1 to 1,000
```{r}
e <- seq(1:1000)
print(e)
```
# a. How many data points from 8.1 to 8.4?
```{r}
length1 <- length(m)
length2 <- length(a)
length3 <- length(r)
length4 <- length(i)
sum(length1+length2+length3+length4)
```
# 143 data points from 8.1 to 8.4.

# b.
```{r}
m <- seq(1:100)
a <- seq(20,60)
r <- mean(20,60)
i <- sum(51:91)
```

# c. For 8.5 find only maximum data points until 10.
```{r}
e <- 1:1000
answer <- max(e[e <- 10])
answer
```

# 9. Vector
```{r}
Filter(function(i) { all(i %% c(3,5,7) != 0) }, seq(100))
```

# 10. Generate a sequence backwards of the integers from 1 to 100.
```{r}
rev(seq(1:100))
```

# 11. Multiples
```{r}
upper_limit <- 25
num <- 1:(upper_limit - 1)
multiples <- num[num %% 3 == 0 | num %% 5 == 0]
multiples
```

# a. How many data points from 10 and 11.
```{r}
length(multiples)
```

# 11 data points from 10 and 11.

b.

